Compartiendo datos en Ecología: como añadir (¿más?) valor a tus datos

### 2019-04-23 ms/tables.Rmd
update
Merge branch 'master' of https://github.com/ajpelu/nota_dataRepositories

```{r}
library(tidyverse)
library(here)
library(pander)
library(kableExtra)
library(knitr)
library(dplyr)
library(flextable)
library(officer)
library(here)
library(xlsx)
# library(ReporteRs)
```

```{r}
d <- read.xlsx(file=here("data", "Table_1.xlsx"), "t1")

t1 <- regulartable(d)

@@

d1 <- d %>% 
  separate(Revista, c("Revista", "Revista_href"), sep = "]") %>%
  separate(URLs.útiles..criterios.de.repositorio., c("CriterioRepo", "CriterioRepo_href"), sep = "]") %>% 
  separate(URLs.útiles..política.de.datos., c("pd", "pd_href"), sep = "]") %>% 
  mutate(Revista = str_sub(Revista, 2)) %>% 
  mutate(CriterioRepo = str_sub(CriterioRepo, 2)) %>% 
  mutate(pd = str_sub(pd, 2)) %>% 
  mutate(Revista_href = str_sub(Revista_href, 2, -2)) %>% 
  mutate(CriterioRepo_href = str_sub(CriterioRepo_href, 2, -2)) %>% 
  mutate(pd_href = str_sub(pd_href, 2, -2))

t1 <- flextable(d1)
tabla1 <- t1 %>% 
  compose(j = "Revista", value = as_paragraph(hyperlink_text(x=Revista, url = Revista_href))) %>% 
  compose(j = "CriterioRepo", value = as_paragraph(hyperlink_text(x=CriterioRepo, url = CriterioRepo_href))) %>% 
  compose(j = "pd", value = as_paragraph(hyperlink_text(x=pd, url = pd_href)))

>>>>

```{r}
library(tidyverse)
library(here)
library(pander)
library(kableExtra)
library(knitr)
library(dplyr)
library(flextable)
library(officer)
library(here)
library(xlsx)
library(openxlsx)
# library(ReporteRs)
```

```{r}
d <- read.xlsx(here::here("data", "Table_1.xlsx"), "t1")

d1 <- d %>% 
  separate("Revista", c("Revista", "Revista_href"), sep = "]") %>%
  separate("URLs.útiles.(criterios.de.repositorio)", c("CriterioRepo", "CriterioRepo_href"), sep = "]") %>% 
  separate("URLs.útiles.(política.de.datos)", c("pd", "pd_href"), sep = "]") %>% 
  mutate(Revista = str_sub(Revista, 2)) %>% 
  mutate(CriterioRepo = str_sub(CriterioRepo, 2)) %>% 
  mutate(pd = str_sub(pd, 2)) %>% 
  mutate(Revista_href = str_sub(Revista_href, 2, -2)) %>% 
  mutate(CriterioRepo_href = str_sub(CriterioRepo_href, 2, -2)) %>% 
  mutate(pd_href = str_sub(pd_href, 2, -2))

t1 <- flextable(d1, col_keys = c("Revista", "Ranking","Revista_href"))
tabla1 <- compose(t1, j = 1, value = as_paragraph(hyperlink_text(x= Revista, url = Revista_href)))

@@

t1 <- flextable(d1)
ft <- display(t1, col_key = "Revista", 
              pattern = "# {{mylink}}",
              formatters = list(mylink ~ hyperlink_text(Revista_href, Revista)))

ft <- display(
    t1, col_key = "col", pattern = "# {{mylink}}",
    formatters = list(mylink ~ hyperlink_text(href, col) )
)
ft

ft <- flextable(head( mtcars, n = 10))
ft <- display(ft, col_key = "carb",
  i = ~ drat > 3.5, pattern = "# {{carb}}",
  formatters = list(carb ~ sprintf("%.1f", carb)),
  fprops = list(carb = fp_text(color="orange") ) )
ft <- autofit(ft)

ft <- display(
    ft, col_key = "col", pattern = "# {{mylink}}",
    formatters = list(mylink ~ hyperlink_text(href, col))
)
ft

t1 <- flextable(d1)
tabla1 <- t1 %>% 
  compose(j = "Revista", value = as_paragraph(hyperlink_text(x="Revista", url = "Revista_href")))

%>% 
  compose(j = "CriterioRepo", value = as_paragraph(hyperlink_text(x="CriterioRepo", url = "CriterioRepo_href"))) %>% 
  compose(j = "pd", value = as_paragraph(hyperlink_text(x="pd", url = "pd_href")))
